Regression Cube Analysis of Cohort Study Data

### 2015-03-20 draft.tex
added parts of Implementation section

\subsection{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.8in]{figures/placeholder}
 \caption{
 \com{Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%
\com{Use VAST'14 as Guideline}
\com{Cloud computing}
\com{Volume Rendering vs Particles}
\com{Speed is merely a matter of available server machines due to parallelization process.}
\com{Security enabled by hashing files.}
\com{Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend (Fig.~\ref{fig:Implementation})}

>>>>

\subsection{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.8in]{figures/placeholder}
 \caption{
 \com{Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%

\paragraph{Front-End.}
The front end is created using \texttt{HTML5}, \texttt{CSS3} and \texttt{Javascript}.
%%
\texttt{Angular.js} abstracts web application into models and views, allowing for a responsive way to combine \texttt{HTML} and \texttt{Javascript}.
%%
\texttt{Angular.js} is forcing developers to write modularized code, which makes the components easier expandable while keeping the code maintainable by including unit tests.
%%
The page layout is handled using \texttt{Twitter Bootstrap}, which also provides a rich set of UI elements with proper stylings.
%%
The 2D mosaic plot is implemented using \texttt{Data driven Documents}(\texttt{D3.js}), which is very popular in information visualization using vector graphics.
%%
It provides fast and easy methods for binding data to graphical elements.
%%
The 3D plot is created using the WebGL-based \texttt{Threejs} library.
%%
We experimented with different ways for achieving the cube representation, including volume rendering, cube primitives for each data point and shader-based solutions.
%% TODO
Using a volume rendering algorithm for the cube \com{TODO}.
%%
Creating a cube primitive for each data point resulted in non-interactive framerates for data sets larger than 30 features (creating 30$^3$ cube primitives).
%%
We use a shader-based solution by rendering the cube as a sprite based particle system, allowing to customize color and opacity of every data point.
%%
It also is the fastest solution that we tested.

\paragraph{Back-End.}
Two server structures serve as back-end.
%%
First, the web-server is written in \texttt{Javascript} using \texttt{NodeJS}, running on Googles V8 Javascript runtime environment.
%%
It is hosted on \texttt{Heroku}, a cloud application platform.
%%

The statistical processors are the second structure.
%%
They rely on the statistical programming language \texttt{R}.
%%
It is widely adopted in the statistical analysis community, yielding a rich support of fast state-of-the-art statistics algorithms as well newly published methods.
%%
\texttt{OpenCPU} provides a API for accessing \texttt{R} via HTTP calls.
%%

\paragraph{Source and Access.}

\com{Use VAST'14 as Guideline}
\com{Cloud computing}
\com{Volume Rendering vs Particles}
\com{Speed is merely a matter of available server machines due to parallelization process.}
\com{Security enabled by hashing files.}
\com{Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend (Fig.~\ref{fig:Implementation})}
